A Topography of Climate Change Research

### 2020-01-31 poster/poster_amld_2020.tex
amld pres

\usepackage{relsize}		% For \smaller
\usepackage{url}			% For \url
\usepackage{epstopdf}	% Included EPS files automatically converted to PDF to include with pdflatex

\usepackage{multicol}

@@

\definecolor{bordercol}{RGB}{40,40,40}
\definecolor{headercol1}{HTML}{DEEEB2}
\definecolor{headercol2}{RGB}{80,80,80}
\definecolor{headerfontcol}{RGB}{0,0,0}
\definecolor{boxcolor}{HTML}{f0f0f0}

@@

%%% General Poster Settings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% Eye Catcher, Title, Authors and University Images %%%%%%%%%%%%%%%%%%%%%%
\begin{poster}{
	grid=false,
	% Option is left on true though the eyecatcher is not used. The reason is
	% that we have a bit nicer looking title and author formatting in the headercol
	% this way
	%eyecatcher=false, 
	borderColor=bordercol,
	headerColorOne=headercol1,
	headerColorTwo=headercol2,
	headerFontColor=headerfontcol,
	% Only simple background color used, no shading, so boxColorTwo isn't necessary
	boxColorOne=boxcolor,
	headershade=plain,
	boxColorTwo=green,
	headershape=roundedright,
	headerfont=\Large\sf\bf,
	textborder=rectangle,
	background=user,
%  	boxshade=shade-lr,
  	headerborder=closed
}
%%% Eye Cacther %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
	Eye Catcher, empty if option eyecatcher=false - unused
}
%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\sf\bf
	A Topography of Climate Change Literature
}
%%% Authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
	\vspace{0.8em} Max Callaghan\\
	{\smaller callaghan@mcc-berlin.net}
}
%%% Logo %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
% The logos are compressed a bit into a simple box to make them smaller on the result
\setlength\fboxsep{0pt}
\setlength\fboxrule{0.5pt}
	\fbox{
		\begin{minipage}{14em}
			\begin{minipage}{7em}
				\centering
			\vspace*{0.005\textheight}
			\includegraphics[width=6.5em]{../pres/MCC_Logo_RZ_rgb.jpg}
			\\
			\vspace*{0.005\textheight}
			\includegraphics[width=6.5em]{../pres/University_of_Leeds_Logo.png}
			\vspace*{0.005\textheight}
			\end{minipage}
			\begin{minipage}{7em}
				\centering
			\includegraphics[width=6.5em]{../pres/logo_hbs.jpg}
			\end{minipage}
		\end{minipage}
	}
}

@@

\includegraphics[width=\linewidth]{../plots/literature_size/pubs_time}

@@

\headerbox{Proportionality}{name=definitions,column=0,below=problem}{
\begin{center}
	\includegraphics[width=0.98\linewidth]{../plots/ipcc_representation/ipcc_rep_oecds_simplified_short.pdf}
\end{center}
\vspace{-1.4em} 
Contrary to suggestions/previously \cite{Victor2015, Bjurström2011}, the social sciences are over-represented in IPCC reports, engineering/agricultural sciences are under-represented
}

@@

\begin{center}
	\includegraphics[width=0.98\linewidth]{../plots/ipcc_representation/ipcc_rep_new1771_all.pdf}
\end{center}

@@

\headerbox{New Concepts}{name=concepts,span=2,column=1,row=0}{
	{\scriptsize
	\input{../tables/growth_table.tex}}

@@

\begin{minipage}{0.74\linewidth}
	\begin{center}
	\includegraphics[width=1\linewidth]{../tsne_results/plots/run_1771_s_0_p200_all_topic_words_oecds_big.png}
	\end{center}
\end{minipage}
\begin{minipage}{0.24\linewidth}
	Using T-SNE \cite{vandermaaten2008}, we can project each document into a 2D space such that documents with similar 100-dimensional topic vectors are close together.

@@

\begin{center}
	\includegraphics[width=0.98\linewidth]{../tsne_results/plots/run_1771_s_0_p200_evolution_4.png}
\end{center}

@@

\headerbox{Social Science \& Solutions}
{name=socSciSol,span=1,column=2,below=density}{
	\begin{center}
		\includegraphics[width=0.98\linewidth]{../plots/run_1771_wg3_socsci.pdf}
	\end{center}
	\vspace{-1.4em}
Those WGIII topics with a higher share of social science documents are better-represented in IPCC. Either the IPCC must engage with the social science literature, or the social sciences must cover solutions-topics.
}

@@

Quantification of knowledge transfer pyramid.

Tools/methodologies for computer assisted evidence synthesis.

>>>>

\usepackage{relsize}		% For \smaller
\usepackage{url}			% For \url
\usepackage{epstopdf}	% Included EPS files automatically converted to PDF to include with pdflatex
\usepackage{moresize}
\usepackage{multicol}

@@

\definecolor{bordercol}{RGB}{40,40,40}
\definecolor{headercol1}{HTML}{DEEEB2}
\definecolor{headercol2}{RGB}{80,80,80}
\definecolor{headerfontcol}{RGB}{0,0,0}
\definecolor{boxcolor}{HTML}{ffffff}

@@

%%% General Poster Settings %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%% Eye Catcher, Title, Authors and University Images %%%%%%%%%%%%%%%%%%%%%%
\begin{poster}{
	grid=false,
	% Option is left on true though the eyecatcher is not used. The reason is
	% that we have a bit nicer looking title and author formatting in the headercol
	% this way
	%eyecatcher=false, 
	borderColor=bordercol,
	headerColorOne=headercol1,
	headerColorTwo=headercol2,
	headerFontColor=headerfontcol,
	% Only simple background color used, no shading, so boxColorTwo isn't necessary
	boxColorOne=boxcolor,
	headershade=plain,
	boxColorTwo=green,
	headershape=roundedright,
	headerfont=\Large\sf\bf,
	textborder=rectangle,
	background=user,
%  	boxshade=shade-lr,
  	headerborder=closed
}
%%% Eye Cacther %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
	Eye Catcher, empty if option eyecatcher=false - unused
}
%%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\sf\bf
	A Topography of Climate Change Research
}
%%% Authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
	\vspace{0.4em} \url{https://dx.doi.org/10.1038/s41558-019-0684-5}\\
	Max Callaghan\\
	{\smaller callaghan@mcc-berlin.net}
}
%%% Logo %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{
% The logos are compressed a bit into a simple box to make them smaller on the result
\setlength\fboxsep{0pt}
\setlength\fboxrule{0.5pt}
	\fbox{
		\begin{minipage}{14em}
			\begin{minipage}{7em}
				\centering
			\vspace*{0.005\textheight}
			\includegraphics[width=6.5em]{../pres/MCC_Logo_RZ_rgb.jpg}
			\\
			\vspace*{0.005\textheight}
			\includegraphics[width=6.5em]{../pres/University_of_Leeds_Logo.png}
			\vspace*{0.005\textheight}
			\end{minipage}
			\begin{minipage}{7em}
				\centering
			\includegraphics[width=6.5em]{../pres/logo_hbs.jpg}
			\end{minipage}
		\end{minipage}
	}
}

@@

\includegraphics[width=\linewidth]{../plots/literature_size/pubs_time_wgb_lp.pdf}

@@

\headerbox{Proportionality}{name=definitions,column=0,below=problem}{
\begin{center}
	\includegraphics[width=0.98\linewidth]{../plots_pub/ipcc_rep_oecds_simplified_lp.pdf}

\end{center}
\vspace{-1.4em} 
Contrary to suggestions/previously \cite{Victor2015, Bjurstroem2011}, the social sciences are over-represented in IPCC reports, engineering/agricultural sciences are under-represented
}

@@

\begin{center}
	\includegraphics[width=0.98\linewidth]{../plots_pub/rep_time_lp.pdf}
\end{center}

\vspace{-1.4em}

@@

\headerbox{New Concepts}{name=concepts,span=2,column=1,row=0}{
	{\scriptsize\resizebox{\textwidth}{!}{
	\input{../tables/growth_table.tex}}}

@@

\begin{minipage}{0.74\linewidth}
	\begin{center}
	\includegraphics[width=1\linewidth]{../plots_pub/all_topic_words_oecds.png}
	\end{center}
\end{minipage}
\begin{minipage}{0.24\linewidth}
	Using T-SNE \cite{vandermaaten2008}, we can project each document into a 2D space such that documents with similar 100-dimensional topic vectors are close together.

@@

\begin{center}
	\includegraphics[width=0.98\linewidth]{../plots_pub/topic_evolution_4.png}
\end{center}

@@

\headerbox{Social Science \& Solutions}
{name=socSciSol,span=1,column=2,below=density}{
	\begin{center}
		\includegraphics[width=0.98\linewidth]{../plots/run_1861_wg3_socsci_lp.pdf}
	\end{center}
	\vspace{-1.4em}
Those WGIII topics with a higher share of social science documents are better-represented in IPCC. Either the IPCC must engage with the social science literature, or the social sciences must cover solutions-topics.
}

@@

Robust Statistical Stopping Criteria for Automated
Screening in Systematic Reviews

### 2020-01-31 pres/2020_01_amld.tex
amld pres

\title[Big Literature]{A Topography of Climate Change Research}
\subtitle{}
\author{Max Callaghan }
\institute[MCC]{
	{\footnotesize with Jan Minx, Piers Forster} \\ \medskip
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg} \hspace{3em}
	\includegraphics[height=1cm]{University-of-Leeds-logo.png}
}
\date{September 26, 2019}

@@

\begin{frame}{What Do We Know About the IPCC?}
\begin{columns}
	\begin{column}{0.618\linewidth}
		\begin{itemize}
			\item<2-> The social sciences are seen as under-represented in IPCC reports
			\item<3-> \citep{Bjurström2011} are often cited as evidence of this under-representation, e.g. as demonstrating ``a powerful bias to the natural sicences in the construction of `IPCC knowledge' '' \cite{Hulme2010}
			\item<4-> The evidence is simply the relative shares of the different disciplines in IPCC citations

@@

	\begin{column}{0.618\linewidth}<1->
		\begin{figure}[h!]
			\begin{center}
				\includegraphics[width=\linewidth]{../plots/run_1861_wg3_socsci.pdf}
			\end{center}
		\end{figure}

@@

\begin{frame}{Conclusions}
\begin{columns}[t]
	\begin{column}{0.618\linewidth}
		\begin{itemize}
			\item<1-> Lack of social science knowledge in IPCC $ \neq $ IPCC natural science bias
			\item<2-> If there is a lack, we need to produce more social science knowledge, particularly on technical solutions
			\item<3-> There is a vast technical literature on solutions which is relatively untapped
		\end{itemize}
	\end{column}
	\begin{column}{0.382\linewidth}<4->
		\textbf{But,}
		\begin{itemize}
			\item<4-> Literature here is not all relevant climate knowledge (only WoS, only directly on climate change)
			\item<5-> Relative representation of different parts of the literature is job of IPCC to decide, not a computer
		\end{itemize}
		\only<6->{\textbf{Nevertheless,}}
		\begin{itemize}
			\item<6-> Computer assisted methods can help the IPCC make its decisions on how to represent the literature from a more solid basis, and efficiently point to areas of growth or of under-representation
		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{n Topics}
\vspace{-0.4cm}
\begin{figure}
	\includegraphics[width=1\linewidth]{../plots_pub/topic_rep_ks_wide.pdf}
\end{figure}

>>>>

\title[Big Literature]{A Topography of Climate Change Research}
\subtitle{}
\author{Max Callaghan }
\institute[MCC]{
	{\footnotesize with Jan Minx, Piers Forster} \\ \medskip
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg} \hspace{3em}
	\includegraphics[height=1cm]{University-of-Leeds-logo.png}
}
\date{January 26, 2019}

@@

\begin{frame}{What Do We Know About the IPCC?}
\begin{columns}
	\begin{column}{0.618\linewidth}
		\begin{itemize}
			\item<2-> The social sciences are seen as under-represented in IPCC reports
			\item<3-> \citep{Bjurstroem2011} are often cited as evidence of this under-representation, e.g. as demonstrating ``a powerful bias to the natural sicences in the construction of `IPCC knowledge' '' \cite{Hulme2010}
			\item<4-> The evidence is simply the relative shares of the different disciplines in IPCC citations

@@

	\begin{column}{0.618\linewidth}<1->
		\begin{figure}[h!]
			\begin{center}
				\includegraphics[width=\linewidth]{../plots/run_1861_wg3_socsci_lp.pdf}
			\end{center}
		\end{figure}

@@

\begin{frame}{Conclusions}
\begin{columns}[t]
	\begin{column}{0.618\linewidth}
		\begin{itemize}
			\item<1-> Lack of social science knowledge in IPCC $ \neq $ IPCC natural science bias
			\item<2-> If there is a lack, we need to produce more social science knowledge, particularly on technical solutions
			\item<3-> There is a vast technical literature on solutions which is relatively untapped
		\end{itemize}

		\bigskip
		\bigskip
		\only<7->{
		\hrule
		\bigskip
		\bigskip
		\hspace{2em}A Topography of Climate Change Research
		\bigskip

		\hspace{2em}\url{https://dx.doi.org/10.1038/s41558-019-0684-5}

		\bigskip
		\hspace{2em}\url{callaghan@mcc-berlin.net}
		}
	\end{column}
	\begin{column}{0.382\linewidth}<4->
		\textbf{But,}
		\begin{itemize}
			\item<4-> Literature here is not all relevant climate knowledge (only WoS, only directly on climate change)
			\item<5-> Relative representation of different parts of the literature is job of IPCC to decide, not a computer
		\end{itemize}
		\only<6->{\textbf{Nevertheless,}}
		\begin{itemize}
			\item<6-> Computer assisted methods can help the IPCC make its decisions on how to represent the literature from a more solid basis, and efficiently point to areas of growth or of under-representation
		\end{itemize}
	\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}{n Topics}
\vspace{-0.4cm}September
\begin{figure}
	\includegraphics[width=1\linewidth]{../plots_pub/topic_rep_ks_wide.pdf}
\end{figure}

### 2020-01-31 pres/AMLD2020_AI&Climate Change_MaxCallaghan_V1.tex
amld pres

\title[Big Literature]{A Topography of Climate Change Research}
\subtitle{}
\author{Max Callaghan }
\institute[MCC]{
	{\footnotesize with Jan Minx, Piers Forster} \\ \medskip
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg} \hspace{3em}
	\includegraphics[height=1cm]{University-of-Leeds-logo.png}
}
\date{January 26, 2019}

@@

@@

\begin{frame}{n Topics}
\vspace{-0.4cm}September
\begin{figure}
	\includegraphics[width=1\linewidth]{../plots_pub/topic_rep_ks_wide.pdf}
\end{figure}

>>>>

\title[Big Literature]{A Topography of Climate Change Research}
\subtitle{}
\author{Max Callaghan }
\institute[MCC]{
	{\footnotesize with Jan Minx, Piers Forster} \\ \medskip
	\includegraphics[height=1cm,width=2cm]{MCC_Logo_RZ_rgb.jpg} \hspace{3em}
	\includegraphics[height=1cm]{University-of-Leeds-logo.png} \hspace{3em}
	\includegraphics[height=1cm]{logo_hbs.jpg}
}
\date{January 27, 2019}

@@

\begin{frame}{WGIII topics with little social science are under-represented}

@@

\begin{frame}{Topic disciplinary entropy and subdiscipline representation}
\vspace{-0.4cm}
\begin{columns}
\begin{column}{0.5\linewidth}
\begin{figure}
	\includegraphics[width=1\linewidth]{../plots_pub/upload_figures/Figure_SI_1.pdf}
\end{figure}
\end{column}

\begin{column}{0.5\linewidth}
	\begin{figure}
		\includegraphics[width=1\linewidth]{../plots_pub/upload_figures/Figure_SI_3.pdf}
	\end{figure}
\end{column}

\end{columns}
\end{frame}

\begin{frame}{Topic growth}
\vspace{-0.4cm}
\begin{figure}
	\includegraphics[width=0.5\linewidth]{../tsne_results/plots/run_1861_s_0_p100_evolution_4.pdf}
\end{figure}

\begin{frame}{Social sciences and topic representation}
\vspace{-0.4cm}
\begin{figure}
	\includegraphics[width=0.5\linewidth]{../plots_pub/upload_figures/Figure_SI_4.pdf}
\end{figure}

\begin{frame}{n Topics}
\vspace{-0.4cm}
\begin{figure}
	\includegraphics[width=1\linewidth]{../plots_pub/topic_rep_ks_wide.pdf}
\end{figure}

### 2020-01-31 pres/AMLD2020_AI&Climate Change_MaxCallaghan_V3.tex
amld pres

\begin{columns}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> Topic modelling \citep{Blei2012} describes a suite of algorithms to discover the latent semantic content of documents
			\item<2-> NMF \citep{Lee1999} is a dimensionality reduction technique that can be used for topic modelling
			\item<3-> Topics are distributions of words. They describe documents.
			\item<4-> A document's topic scores describe its association with each topic

@@

	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> The physical science of climate change is older and better covered
			\item<2-> Topics on ``solutions'' (although rather technical than policy) are newer and under-represented
			\item<3-> Newer WGII topics are better covered than newer WGIII topics

>>>>

\begin{columns}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> Topic modelling \citep{Blei2012} describes a suite of algorithms to discover the latent semantic content of documents
			\item<2-> NMF \citep{Lee1999} is a dimensionality reduction technique that can be used for topic modelling
			\item<2-> Topics are distributions of words. They describe documents.
			\item<2-> A document's topic scores describe its association with each topic

@@

	\end{column}
	\begin{column}{0.382\linewidth}
		\begin{itemize}
			\item<1-> The physical science of climate change is older and better covered
			\item<1-> Topics on ``solutions'' (although rather technical than policy) are newer and under-represented
			\item<1-> Newer WGII topics are better covered than newer WGIII topics
